#loading ggvis for data visualization

```{r}
library(corrplot)
library(caret)
```


#loading the dataset

```{r}
data <- read.csv('C:/Users/paipr/Desktop/ME315 Project/task/Dataset/processed.cleveland.data', sep = ",")
```

#head(data)

#renaming the columns (features)
```{r}
colnames(data)<-c("age", "gender", "cp", "trestbps", "chol", "fbs", "restecg",
               "thalach", "exang", "oldpeak", "slope", "ca","thal", "num")
head(data)
data$num[data$num==1 | data$num==2 | data$num==3 | data$num==4]<-1
```

#checking the number of examples per class
```{r}
table(data$num)

summary(data)
str(data)
data$num <- as.factor(data$num)
```
#str(data)
#Correlation analysis of the data
```{r}
df<-data.matrix(data)

cor <- cor(df)

corrplot(cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)

set.seed(1234)
```

#splitting the dataset into 70:30 ratio
```{r}
trainIndices = createDataPartition(data$num, p=0.7)$Resample1

trainData <- data[trainIndices,]
testData <- data[-trainIndices,]

print(trainData[,14])
print(testData[,14])
```
#names(getModelInfo())
#str(trainData)
#str(testData)

```{r}
model_logReg <- train(as.factor(num) ~ ., data = trainData, method="glm", family="binomial")

predictions_train<-predict(object=model_logReg,trainData)
confusionMatrix(predictions_train,trainData$num)

predictions<-predict(object=model_logReg,testData)
```


# Evaluate the predictions
```{r}
table(predictions)
```


# Confusion matrix 
```{r}
confusionMatrix(predictions,testData$num)

model_rf <- train(as.factor(num) ~ ., data = trainData, method="rf")

predictions_rf_train<-predict(object=model_rf,trainData)
```


# Evaluate the predictions
```{r}
table(predictions_rf_train)
```

# Confusion matrix 
```{r}
confusionMatrix(predictions_rf_train,trainData$num)

predictions_rf<-predict(object=model_rf,testData)
```


# Evaluate the predictions
```{r}
table(predictions_rf)
```

# Confusion matrix 
```{r}
confusionMatrix(predictions_rf,testData$num)
```

